Group meetings

### 2023-06-26 diapo/26-06-23_meeting/main.tex
Updated pres for tonight

  \begin{frame}{What's new}
    Here the scale factor is almost the same with the serialized and parallel version ( 1.50 vs 1.58 ).
    \includegraphics[width=\textwidth]{output/factor1.5.png}
  \end{frame}

>>>>

  \begin{frame}{What's new}
    Here the scale factor is almost the same with the serialized and parallel version (1.50 vs 1.58).
    \includegraphics[width=\textwidth]{output/factor1.5.png}
  \end{frame}

  \begin{frame}{What's new}
    Today, I managed to reduce the scale factor even more. (1.21)
    \includegraphics[width=\textwidth]{output/factor1.2.png}
  \end{frame}
